### 2023-08-22 paper/sec-results.tex
some work on Sect 3.2

>>>>

Add also statistical estimators, and plots of PDF uncertainty only.
%
Maybe also reduction of PDF luminosities, as relevant for phenomenology.

Fig.~\ref{fig:nnpdf40_fpf_lumis} displays a comparison of the PDF luminosities at $\sqrt{s}=13$ TeV
  as a function of the final-state invariant mass $m_X$ between
  the baseline NNPDF4.0 NNLO determination and its variant which includes
  the FPF pseudo-data from the FASER$\nu$2, FLArE100, and AdvSND experiments.
  %
  Results are shown normalised to the central value of the NNPDF4.0 baseline.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\centering
\includegraphics[width=0.45\textwidth]{plots/qqlumi_nnpdf40_allfpf.pdf}
\includegraphics[width=0.45\textwidth]{plots/qqbarlumi_nnpdf40_allfpf.pdf}
\includegraphics[width=0.45\textwidth]{plots/udbarlumi_nnpdf40_allfpf.pdf}
\includegraphics[width=0.45\textwidth]{plots/dubarlumi_nnpdf40_allfpf.pdf}
\caption{Comparison of the PDF luminosities at $\sqrt{s}=13$ TeV
  as a function of the final-state invariant mass $m_X$ between
  the baseline NNPDF4.0 NNLO determination and its variant which includes
  the FPF pseudo-data from the FASER$\nu$2, FLArE100, and AdvSND experiments.
  %
  Results are shown normalised to the central value of the NNPDF4.0 baseline.
%
}
\label{fig:nnpdf40_fpf_lumis}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
